Supplementary Material

### 2021-04-16 paper/ifo-supplementary-material.tex
going through more comments
fixing and combining plots - part 2

\begin{figure*}
	\includegraphics[width=0.59\textwidth]{figures/setup_pic2.pdf}
	\includegraphics[width=0.4\textwidth]{figures/circuit_pic3.pdf}
	\caption{
Left: A photograph of the optical microphone with an inset of the photodiode. The Michelson interferometer is shown on the left and the circuit and Raspberry Pi on the right. In the main image, the photodiode is placed behind a cloth screen as explained in the main article. The inset shows a face-on view of the photodiode with the cloth screen removed. 
Right: A photograph of the photodiode circuit assembled on a breadboard. The leads from the photodiode enter from the left of the picture. The Raspberry Pi is shown at the top of the picture.
}
	\label{fig:photographs_of_optical_microphone_and_circuit}
\end{figure*}

@@

\begin{figure*}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
    % height=0.5\textheight,trim={1cm 4.5cm 0.4cm 3.5cm},clip
	\includegraphics[width=.8\textwidth, trim={1cm 3cm 1cm 1cm}]{figures/notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:BackgroundNotchWienerCombined}
	Timeseries (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
    The source signal, shown in the first row, is a $1\,{\rm s}$ recording of an adult male voice (saying ``A cathode ...''). 
    The source signal is shifted by $0.12\,{\rm s}$ to the right to synchronise the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
	The second row shows the raw output from the optical microphone when the input signal from the first row is played. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=.49\textwidth]{figures/psd_butterworth_14_6.pdf}
	\caption{\label{fig:psd_noise}
Top: power spectral density (PSD) of background noise from the optical microphone (with the speaker off). 
Bottom: the PSD after applying a Butterworth bandpass filter (bottom panel) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise, the PSD is fairly white. 
After filtering we see strong attenuation (at least 3~dB) of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}

@@

\label{sec:notch}
\begin{figure*}
\begin{center}
\includegraphics[width=.9\textwidth]{figures/notch_filter_response.jpg}
\end{center}
\caption{\label{fig:notchMagResponse}
Amplitude (magnitude) response for the first five notches of fifteen for the cascaded notch filter described by Eqs.~\ref{eqn:notch} and~\ref{eqn:notch15}. 
}
\end{figure*}

@@

\begin{figure*}
	%\includegraphics[width=0.49\textwidth]{figures/combined_timeseries_melatos_shift_source.pdf}
	%\includegraphics[width=0.49\textwidth]{figures/combined_spectrum_melatos.pdf}
    \includegraphics[height=0.57\textheight]{figures/combined_timeseries_melatos_shift_source_tall.pdf}
    \includegraphics[height=0.57\textheight]{figures/combined_spectrum_melatos_tall.pdf}
    \caption{\label{fig:logMMSE_timeseries_freqspectrum}
Timeseries (left column) and frequency spectrum (right columns) results with the logMMSE estimator. 
The original source signal and optical microphone recording in the top and middle panels respectively are for comparison and are identical to those shown in the top two panels in Fig.~\ref{fig:BackgroundNotchWienerCombined} (again, the source signal is shifted by $0.12\,{\rm s}$). 
The bottom-left panel shows the timeseries of the recording after filtering with the logMMSE estimator, where the rise at the start of the timeseries is expected when filtering a signal of finite duration.
The bottom-right panel shows the corresponding frequency spectrum with the logMMSE estimator. 
The spectrum shows only a detail of the total frequency domain (there is little activity at higher frequencies) and has truncated peaks at amplitude $2$ which otherwise dominate the plot. 
The change in scale from the top panel is not of concern as the ear hears the relative frequency content and normalisation of the timeseries fixes any scaling. 
    }
\end{figure*}

>>>>

\begin{figure*}
	\includegraphics[height=0.41\textwidth]{figures/setup_pic2.pdf}
	\includegraphics[height=0.41\textwidth]{figures/circuit_pic3.pdf}
	\caption{
Left: A photograph of the optical microphone with an inset of the photodiode. The Michelson interferometer is shown on the left and the circuit and Raspberry Pi on the right. In the main image, the photodiode is placed behind a cloth screen as explained in the main article. The inset shows a face-on view of the photodiode with the cloth screen removed. 
Right: A photograph of the photodiode circuit assembled on a breadboard. The leads from the photodiode enter from the left of the picture. The Raspberry Pi is shown at the top of the picture.
}
	\label{fig:photographs_of_optical_microphone_and_circuit}
\end{figure*}

@@

\begin{figure*}
	\begin{center}
    %% trim order is <left> <lower> <right> <upper>
    % height=0.5\textheight,trim={1cm 4.5cm 0.4cm 3.5cm},clip
	\includegraphics[width=.8\textwidth, trim={1cm 3cm 1cm 1cm}]{figures/notch_and_wiener_superplot_v2.pdf}
	\end{center}
	\caption{\label{fig:BackgroundNotchWienerCombined}
	\jam{Fig.2 should be combined with Fig.6 using combined\_results\_full\_melatos\_labelled.pdf}
	Timeseries (left column) and frequency spectrum (right column) results for the background subtraction, notch, and Wiener filters.
    The source signal, shown in the first row, is a $1\,{\rm s}$ recording of an adult male voice (saying ``A cathode ...''). 
    The source signal is shifted by $0.12\,{\rm s}$ to the right to synchronise the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
	The second row shows the raw output from the optical microphone when the input signal from the first row is played. 
    The third row shows a background noise recording from the optical microphone when no audio signal is played. 
    The fourth row shows the result of subtracting the background noise spectrum in the third row from the recording in the second row. 
	The fifth, sixth, and seventh rows show the results of applying the notch filter, the Wiener filter, and both combined, respectively.
	}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=.45\textwidth]{figures/psd_butterworth_14_6.pdf}
	\caption{\label{fig:psd_noise}
Top: power spectral density (PSD) of background noise from the optical microphone (with the speaker off). 
Bottom: the PSD after applying a Butterworth bandpass filter (bottom panel) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise, the PSD is fairly white. 
After filtering we see strong attenuation (at least 3~dB) of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}

@@

\label{sec:notch}
\begin{figure}
\begin{center}
\includegraphics[width=.45\textwidth]{figures/cascaded_notch_response_plot.pdf}
\end{center}
\caption{\label{fig:notchMagResponse}
Amplitude (magnitude) response for the first five notches of fifteen for the cascaded notch filter described by Eqs.~\ref{eqn:notch} and~\ref{eqn:notch15}. 
}
\end{figure}

@@

\begin{figure*}
	%\includegraphics[width=0.49\textwidth]{figures/combined_timeseries_melatos_shift_source.pdf}
	%\includegraphics[width=0.49\textwidth]{figures/combined_spectrum_melatos.pdf}
    \includegraphics[height=0.57\textheight]{figures/combined_timeseries_melatos_shift_source_tall.pdf}
    \includegraphics[height=0.57\textheight]{figures/combined_spectrum_melatos_tall.pdf}
    \caption{\label{fig:logMMSE_timeseries_freqspectrum}
\jam{Fig.2 should be combined with Fig.6 using combined\_results\_full\_melatos\_labelled.pdf}    
Timeseries (left column) and frequency spectrum (right columns) results with the logMMSE estimator. 
The original source signal and optical microphone recording in the top and middle panels respectively are for comparison and are identical to those shown in the top two panels in Fig.~\ref{fig:BackgroundNotchWienerCombined} (again, the source signal is shifted by $0.12\,{\rm s}$). 
The bottom-left panel shows the timeseries of the recording after filtering with the logMMSE estimator, where the rise at the start of the timeseries is expected when filtering a signal of finite duration.
The bottom-right panel shows the corresponding frequency spectrum with the logMMSE estimator. 
The spectrum shows only a detail of the total frequency domain (there is little activity at higher frequencies) and has truncated peaks at amplitude $2$ which otherwise dominate the plot. 
The change in scale from the top panel is not of concern as the ear hears the relative frequency content and normalisation of the timeseries fixes any scaling. 
    }
\end{figure*}
